Five-dimensional seismic data reconstruction using the optimally damped rank-reduction method

### 2020-11-06 odrr5d/paper.tex
2020年11月 6日 星期五 10时11分21秒 CST

%
%\inputdir{hyper}
%\multiplot{3}{hyper-clean-xy,hyper-noisy-xy,hyper-obs-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. The blanks in (c) indicate where there are missing traces. }
%\multiplot{6}{hyper-rr-xy,hyper-drr-xy,hyper-odrr-xy,hyper-rr2-xy,hyper-drr2-xy,hyper-odrr2-xy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}. }
%
%\multiplot{6}{hyper-rr-xy-simi,hyper-drr-xy-simi,hyper-odrr-xy-simi,hyper-rr2-xy-simi,hyper-drr2-xy-simi,hyper-odrr2-xy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }

>>>>

\inputdir{hyper}
\multiplot{3}{hyper-clean-hxhy,hyper-noisy-hxhy,hyper-obs-hxhy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. (a) Clean data. (b) Noisy data. (c) Incomplete data. The blanks in (c) indicate where there are missing traces. }
\multiplot{6}{hyper-rr-hxhy,hyper-drr-hxhy,hyper-odrr-hxhy,hyper-rr2-hxhy,hyper-drr2-hxhy,hyper-odrr2-hxhy}{width=0.3\textwidth}{Common midpoint gather comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The SNR comparisons are shown in Table \ref{tbl:hyper}. }

\multiplot{6}{hyper-rr-hxhy-simi,hyper-drr-hxhy-simi,hyper-odrr-hxhy-simi,hyper-rr2-hxhy-simi,hyper-drr2-hxhy-simi,hyper-odrr2-hxhy-simi}{width=0.3\textwidth}{Local similarity comparison for the synthetic example with hyperbolic events. Top row shows results when $rank=12$. Bottom row shows results when $rank=24$. Left: Reconstructed data using the RR method. Middle: Reconstructed data using the DRR method. Right Reconstructed data using the ORR method. The introduction of local similarity is given in \cite{yangkang2015ortho}. }
